\section{App design}

The \textbf{Karma} application is crafted to provide a simple, motivating, and accessible user experience.

\subsection{Main Screen Design}

As shown in \autoref{fig:main_screen_design}, the main screen acts as the entry point of the app. The user's profile and total Karma Points appear at the top, providing an immediate sense of progress. The layout is intentionally minimal to ensure accessibility.

Functionally, it provides direct access to the next areas:

\begin{itemize}
    \item \textbf{Missions}: Browse or create tasks that grant Karma Points.
    \item \textbf{Karma Board}: Compare personal progress with the rest of the community.
    \item \textbf{Step Counter}: Earn Karma Points passively through physical activity.
    \item \textbf{Motivational Quotes}: Rotating quotes that encourage positive behavior.
\end{itemize}

This combination of clarity, motivational cues, and real-time updates keeps the experience straightforward and engaging.

\subsection{Leaderboard and Statistics Screen}

The layout in \autoref{fig:leaderboard_statistics_screen_design} emphasizes easy interpretation of community progress. Its design uses simple, high-contrast graphs to provide quick insights into user performance.

It includes two main visual elements:

\begin{itemize}
    \item \textbf{Leaderboard}: A horizontal comparison of Karma Points among users.
    \item \textbf{Temporal chart}: A line graph showing how Karma evolves globally over time.
\end{itemize}

These visualizations reinforce the social and competitive aspects of the app while maintaining readability.

\subsection{Missions Screen}

As illustrated in \autoref{fig:missions_screen_design}, the missions screen presents a scrollable \textbf{list of missions}, organized to avoid visual clutter and make browsing intuitive. Each mission is displayed as a clear, self-contained item, and a button allows \textbf{creating new missions}.

This design encourages frequent participation and supports the community-driven nature of the app.

\subsection{Profile Screen}

The profile layout in \autoref{fig:profile_screen_design} gathers the user's personal progress in one place. It highlights essential information such as the \textbf{Total Karma Points}, \textbf{completed or published missions}, and a \textbf{step-history chart}.

By combining achievements and activity over time, this screen strengthens long-term motivation and reinforces the app's gamified approach.
